---
title: "Clique visualization with igraph"
author: "Sean Whalen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{clique-visualization}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The 'cliqueR' package can quickly compute the maximum clique of a graph, as well as enumerate cliques and paracliques of various sizes. Visualizing these results is outside the scope of the package, but can easily be achieved by using the 'igraph' package. Note that the igraph package already supports some clique finding functions: maximal and maximum, but not paraclique. 

## Highlight the maximum clique of a graph

Read in an edgelist graph file. Graphs formatted for 'cliqueR' are prepended by the number of vertices and egdges, so discard the first line when loading into a 'graph' object. 

```{r, results="hide", warning=FALSE, message=FALSE}
library(igraph)
library(cliqueR)
path = system.file("extdata","small_sparse",package="cliqueR")
data = read.table(path)
g = graph_from_data_frame(data[-c(1),], directed = FALSE)
```

Calculate the maximum clique

```{r}
mc = cliqueR.maximum(path)
mc
```

Recolor the vertices comprising the maximum clique 

```{r, fig.show='hold'}
V(g)$color = "white"
V(g)[unlist(mc)]$color = "red"
clique = V(g)[unlist(mc)]
E(g)$color = "grey"
E(g)[clique %--% clique]$color = "red"

sg = induced_subgraph(g, V(g)[unlist(mc)])
V(sg)$color = "red"
plot(g, vertex.size=10, vertex.label=NA, main="graph")
plot(sg, vertex.size=10, vertex.label.dist=3, main="max clique")

```

## Highlight all cliques, coloring by size

Use the profile option to find out how many different sizes of cliques there are, then use that information to generate a list of colors. 

```{r}
profile = cliqueR.maximal(path, profile=1)
num_colors = length(profile)
colors = colorRampPalette(c("#00ff04", "#ff0000"))(num_colors)
colors
```


Find the cliques and plot them. They are ordered by size, so everytime a new clique size is detected move on to the next color and plot the graph for the previous clique size. 
```{r}
V(g)$color = "white"
E(g)$color = "grey"

cliques = cliqueR.maximal(path)

i=1
prev=length(cliques[[1]])
for (cl in cliques) {
  if (length(cl) != prev) {
    i = i + 1
    prev = length(cl)
    plot(g, vertex.size=10, vertex.label=NA, main=paste("size: ", length(cl)-1))
    V(g)$color = "white"
    E(g)$color = "grey"
  }
  V(g)[unlist(cl)]$color = colors[i]
  E(g)[cl %--% cl]$color = colors[i]
}
plot(g, vertex.size=10, vertex.label=NA, main=paste("size: ", length(cl)))

```
